Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-07 ms.tex
correct rprs, NextGen spectrum

\subsection{Transmission Spectrum}
Each phase curve observation includes a transit of WASP-103b. To measure the wavelength-dependent transit depths (the transmission spectrum), we select a subset of each phase curve. The subset includes the transit and additional baseline on either side, such that the total light curve has twice the duration of the transit. Over this short duration, there is negligible curvature in the light curve due to the planet's thermal phase variation. We fit the data with a transit model, which has free parameters for the planet-to-star radius and a linear limb darkening parameter. We fit for the instrument systematics using the same parameters as the phase curve fits, except that we modeled the visit-long systematic as a linear trend in time (which is sufficient for the shorter duration). The advantage of fitting the transits separately from the full phase curves is that the resultant transit depths are not dependent on how the phase variation is modeled. We do not model the transit in the \Spitzer\,$3.6\mu$m channel, since it is challenging to robustly estimate the contribution of correlated noise in the subset of data we model here.  FIXME

We show the measured transmission spectrum in Figure,\ref{fig:tspec}.  The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth. We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1063. We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:FIXME}). We also show the uncorrected transit depths. For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights, much larger than expected from theoretical models. FIXME show GCM in this figure. Water abundance?

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature. The gray points correspond to no correction for the nightside flux. The blue and red points are the corrected for an average nightside photospheric temperature is 1400 and 2000 K, respectively. The atmospheric scale height assumes FIXME.}
\label{fig:tspec}
\end{figure}

>>>>

\subsection{Transmission Spectrum}
Each phase curve observation includes a transit of WASP-103b. To measure the wavelength-dependent transit depths (the transmission spectrum), we select a subset of each phase curve. The subset includes the transit and additional baseline on either side, such that the total light curve has twice the duration of the transit. Over this short duration, there is negligible curvature in the light curve due to the planet's thermal phase variation. We fit the data with a transit model, which has free parameters for the planet-to-star radius and a linear limb darkening parameter. We fit for the instrument systematics using the same parameters as the phase curve fits, except that we modeled the visit-long systematic as a linear trend in time (which is sufficient for the shorter duration). The advantage of fitting the transits separately from the full phase curves is that the resultant transit depths are not dependent on how the phase variation is modeled. %We do not model the transit in the \Spitzer\,$3.6\mu$m channel, since it is challenging to robustly estimate the contribution of correlated noise in the subset of data we model here.  FIXME

We show the measured transmission spectrum in Figure,\ref{fig:tspec}.  The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth. We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1063. We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:models}). We also show the uncorrected transit depths. For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights, much larger than expected from theoretical models. FIXME show GCM in this figure. Water abundance?

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature. The gray points correspond to no correction for the nightside flux. The blue and red points are the corrected for an average nightside photospheric temperature is 1400 and 2000 K, respectively. The atmospheric scale height is $5.5\times10^6$ m, assuming a mean molecular weight of 2.3 amu, surface gravity $g = 15.85 m/s^2$, and a temperature $T = 2410$ K.}
\label{fig:tspec}
\end{figure}
